### 2010-02-26 trunk/deliverables/D2_2_Ontology/classes.tex
the final version that will be submitted to the EC. Mainly revised ontology code, introduction and conclusion
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@603 d8b0c59b-6544-0410-94d9-83a5658a058e

\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasPattern}}{subs:hasPattern}, \htmlref{\texttt{fgo:isPositive}}{subs:isPositive} \\ \hline

>>>>

\textcolor{white}{\textbf{in\_domain\_of}} & \htmlref{\texttt{fgo:hasPattern}}{subs:hasPattern}, \htmlref{\texttt{fgo:hasPatternString}}{subs:hasPatternString}, \htmlref{\texttt{fgo:isPositive}}{subs:isPositive} \\ \hline
